Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
Remove old section comments

%%% this stuff is now in section 3 mostly
%\subsection{Applicability to the Milky Way} \label{ssec:is_it_real}
%As we briefly discussed in Section~\ref{ssec:cosmozoom}, cosmological zoom-in
%simulations of Milky Way-mass galaxies are not perfect representations of the
%Milky Way, and do not reproduce every available observation of the Milky Way.
%For instance, the velocity dispersion-age relation in \mi , \mf , and \mm\ is
%closer to that of M31 \citep{2018arXiv180610564S}.
%
%In order to assess the applicability of our work to the real Milky Way, we
%consider a subset of Table~3 from \citet{2018arXiv180610564S} --- our
%Table~\ref{tab:scale_height} shows the stellar scale heights of \mi , \mf ,
%and \mm\ and the current best estimates for the Milky Way. One noticeable
%feature is that the FIRE galaxies are more ``puffy'' than the Milky Way.
%\Gus{Maybe FIRE collaboration has some insight into the mechanism for this?}.
%This would seem to suggest that the midplane estimates from
%Figure~\ref{fig:midplane} over-estimate the true variation in the Milky Way.

%Another important aspect to consider when comparing the simulated galaxies to
%the Milky Way is the environment/merger history. For instance, \mi\ and \mm\
%both lack a massive neighbor analogous to the LMC. On the other hand, \mf\ has
%had a recenter merger with \Gus{something}. \Gus{Expand more here - how to
%incorporate merger trees?}

%\subsection{Impact on Milky Way observations} \label{ssec:impact_on_mw}
\subsection{The size of the Solar neighborhood} \label{sssec:neighborhood}

Given a local coordinate system, the amplitude and characteristic length scale
of the density fluctuations in the Galactic disk will determine how far this
system can be extended before introducing $\mathcal{O}(1)$ systematic errors
in the computation of actions for thin-disk stars. We consider this a
criterion for the region around the Sun where the analysis of the action-space
distribution of stars on quasi-circular orbits, and therefore the epicyclic
approximation, can be expected to be valid. This leads to a somewhat
dynamically motivated definition of the ``solar neighborhood.''

>>>>

\subsection{The size of the Solar neighborhood} \label{sssec:neighborhood}
Given a local coordinate system, the amplitude and characteristic length scale
of the density fluctuations in the Galactic disk will determine how far this
system can be extended before introducing $\mathcal{O}(1)$ systematic errors
in the computation of actions for thin-disk stars. We consider this a
criterion for the region around the Sun where the analysis of the action-space
distribution of stars on quasi-circular orbits, and therefore the epicyclic
approximation, can be expected to be valid. This leads to a somewhat
dynamically motivated definition of the ``solar neighborhood.''
